---
title: "Scratch Notebook"
output:
  html_notebook:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float: true
---

This notebook is a place to fiddle with ideas before implementing code.

# Simulation framework

* Need to create some sort of object which specifies:
    * A possibly quite complex, nonparametric distribution of scores
    * A possibly quite complex, nonparametric expected outcome as a function of score
    
* Use cases:
    * Extract expected outcome as a function of score.
    This is the target relationship to be recovered by calibration.
    * Random sample of scores from the distribution,
    with randomly realised outcomes.
    This is the input data for calibration.

* Specifiy a list of components to be added (result is essentially a mixture of distributions)
* Each component consists of a:
    * Weight (specifies the weight for mixing the components)
    * Distribution of scores
    * Mapping from scores to expected outcome
        * Expected outcome on natural log-odds scale
* Scores mapped to discrete delivery scale        
* Result is a data frame of delivery scale scores
    * Score range is finite (known lower and upper bound)
    * Scores are dense (no gaps between scores)
    * Each score has a relative frequency (for generating instances)
    * Each score has an expected outcome probabilitiy (for plotting true score-outcome relationship
    and generating realised outcomes)

# Distributions of scores

I need continuous distributions of scores and discrete distributions of scores.

## Continuous distributions 

Look at using skew-t distributions to model continuous score distributions.

```{r}
library(sn)
library(tidyverse)

n <- 1e6

d <- tibble(x = rst(n, xi=0, omega = 1, alpha = -3, nu = 9))

d %>% ggplot() +
  geom_histogram(aes(x = x), bins = 100) + 
  scale_y_sqrt()

summary(d$x)
```

That looks like a nice set of default skewness parameters.

Try looking at extreme quantiles.

```{r}
q <- qst(p = c(0.0001, 0.001, 0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99, 0.999, 0.9999), xi=0, omega = 1, alpha = -3, nu = 9)
q
```

Invert that.

```{r}
pst(x = q, xi=0, omega = 1, alpha = -3, nu = 9)
```

Get the densities

```{r}
dst(x = q, xi=0, omega = 1, alpha = -3, nu = 9)
```

Random draw of a small number of cases.

```{r}
n <- 20

d <- tibble(x = rst(n, xi=0, omega = 1, alpha = -3, nu = 9))

d %>% ggplot() +
  geom_histogram(aes(x = x), bins = 100) + 
  scale_y_sqrt()

```

